In this lab I used five different methods to solve the one dimensional wave equation
\begin{equation}\label{eq:wave}
	\frac{\partial^2 u}{\partial t^2} = c^2 \frac{\partial^2 u}{\partial x^2}, \qquad 0\le x \le L
\end{equation}
where $c$ is the propagation speed of the wave, $u=u(x,t)$ is the displacement from equilibrium.
The initial and boundary conditions to be solved for are
\begin{equation}\label{eq:initial}
\begin{aligned}%{rcl}
	u(0,t) & = u(L,t) = 0 \\
	u(x,0) & = f(x) \\
	\dot{u}(x,0) & = 0
\end{aligned}
\end{equation}
where $f(x)$ is a known function.

From now on we discretize $u$ in both time, $t$, and space, $x$. So that
\begin{equation}
\begin{aligned}
	u(j \Delta x, n \Delta t) = u_j^n \\
	j = 0, 1, \dots, J=10/\Delta x \\
	n = 0, 1, \dots, N=T/\Delta t \\
\end{aligned}
\end{equation}
where $\Delta x$ and $\Delta t$ are constants chosen so that $N$ and $J$ are integers.

\subsection{Simple Explicit Method}\label{sec:explicit}
This method is also known as \emph{Forward in time, centred in space} (FTCS).
Eq. \eqref{eq:wave} can be rewritten in discretized form as
\begin{equation}
\frac{u_{j}^{n+1} - 2 u_{j}^{n} + u_{j}^{n-1}}{\Delta t^2} = c^2 \frac{u_{j+1}^{n} - 2 u_{j}^{n} + u_{j-1}^{n}}{\Delta x^2}.
\end{equation}
Solving this for $u_{j}^{n+1}$ gives the updating scheme.
%\begin{equation}
%u_{j}^{n+1} = 2 u_{j}^{n} - u_{j}^{n-1} + \frac{c^2\Delta t^2}{\Delta x^2} \left( u_{j+1}^{n} - 2 u_{j}^{n} + u_{j-1}^{n} \right).
%\end{equation}


\subsection{Fully Implicit Method}\label{sec:implicit}
For the implicit method we discretize eq. \eqref{eq:wave} having the spacial derivative calculated forward in time like
\begin{equation}\label{eq:implicit}
\frac{u_{j}^{n+1} - 2 u_{j}^{n} + u_{j}^{n-1}}{\Delta t^2} = c^2 \frac{u_{j+1}^{n+1} - 2 u_{j}^{n+1} + u_{j-1}^{n+1}}{\Delta x^2}.
\end{equation}
Solving this for $u_{j}^{n+1}$ gives the updating scheme.
%\begin{equation}
%u_{j}^{n+1} \left(1 + \frac{c^2\Delta t^2}{\Delta x^2}\right) - \frac{1}{2}\frac{c^2\Delta t^2}{\Delta x^2} \left[ u_{j+1}^{n+1}+u_{j-1}^{n+1} \right] = 2 u_{j}^{n} - u_{j}^{n-1}.
%\end{equation}


\subsection{The Crank-Nicholson Method}\label{sec:crank}
The \emph{Crank-Nicholson} method is similar to the implicit method except that the average in time in both LHS and RHS of eq. \eqref{eq:implicit} should be the same. In order to accomplish this, take the average of the spacial derivative forwards and backwards in time. So that 
\begin{equation}\label{eq:crank}
\frac{u_{j}^{n+1} - 2 u_{j}^{n} + u_{j}^{n-1}}{\Delta t^2} = \frac{c^2}{2} 
\frac{(u_{j+1}^{n+1}+u_{j+1}^{n-1}) - 2 (u_{j}^{n+1}+u_{j}^{n-1}) + (u_{j-1}^{n+1}+u_{j-1}^{n-1})}{\Delta x^2}.
\end{equation}
Solving this for $u_{j}^{n+1}$ gives the updating scheme.
%\begin{equation}
%u_{j}^{n+1} \left(1 + \frac{c^2\Delta t^2}{\Delta x^2}\right) - \frac{1}{2}\frac{c^2\Delta t^2}{\Delta x^2} \left[ u_{j+1}^{n+1}+u_{j-1}^{n+1} \right] = 2 u_{j}^{n} - u_{j}^{n-1}.
%\end{equation}


\subsection{FFT Time-step Method in Normal Space}\label{sec:ffttime}
The updating scheme for this problem was derived in \cite{FDNotes} for time-stepping in 
normal space.

\subsection{Immediate FFT Method}\label{sec:fftimm}
The numerical solution for this method was derived in \cite{FDNotes}.




